Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}

### 2013-03-29 W13report.tex
Filled in correlation writeup

\section{Results: Correlation with KernelCandidate Statistics {\bf ANDYB}}

@@

For postfiltering, Figure~\ref{corrpost} indicates that these metrics
correlate strongly with each other, meaning there is likely little
advantage to looking at more than one metric.  The deconvolution visit
in {\it red} is a clear outlier in this distribution.  While there is
a relationship between the values of these metrics and the numbers of
false positives, it is relatively flat until $\sim 100$ false
detections per sensor; the scatter below this threshold is similar to
the trend, meaning there is no single metric studied that may be used
to predict the numbers of false detections during the fitting process,
within the range of interest ($<10$ false detections per sensor).

For prefiltering, Figure~\ref{corrpre}, {\bf WRITE ME}.

>>>>

\section{Results: Correlation with KernelCandidate Statistics}

@@

For postfiltering, Figure~\ref{corrpost} indicates that these metrics
correlate strongly with each other, meaning there is likely little
advantage to looking at more than one metric.  The deconvolution visit
in {\it red} is a clear outlier in this distribution.  While there is
a relationship between the values of these metrics and the numbers of
false positives, it is relatively flat until $\sim 10^2$ false
detections per sensor; the scatter below this threshold is similar to
the trend, meaning there is no single metric studied that may be used
to predict the numbers of false detections during the fitting process,
within the range of interest ($<10$ false detections per sensor).

For prefiltering, Figure~\ref{corrpre}, the slope between $10^0$ and
$10^1$ false detections is steeper, but still commensurate with the
scatter within that range.  The metrics are still strongly correlated
with each other, but not to the degree as for the postfiltered
statistics.  A less--noisy relationship may be obtained through a
linear combination of these metrics, but we have not fully
investigated this option.  As a summary, these statistics clearly
correlate with the numbers of false positives, and we plan to quantify
these correlations in further detail as we continue our work in Summer
2013.
